Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

\noindent A spatial nested cross-validation on the plot level was chosen to reduce the influence of spatial autocorrelation as much as possible \cite{schratz2019, sperrorest}.
Each plot served as one fold within the cross-validation setting, resulting in four iterations total.
For the inner level (hyperparameter tuning), \(y - 1\) folds were used (with \(y\) being the number of plots).

>>>>

\noindent A spatial nested cross-validation on the plot level was chosen to reduce the influence of spatial autocorrelation as much as possible \cite{schratz2019, sperrorest}.
The \ac{RMSE} was chosen as the error measure.
Each plot served as one fold within the cross-validation setting, resulting in four iterations in total.
For the inner level (hyperparameter tuning), \(k - 1\) folds were used where \(k\) is the number of plots.
